Counterfactual Training: Teaching Models Plausible and Actionable Explanations

### 2025-03-15 paper/preprint/paper.tex
ok now

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-train-default}: Training Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-eval-default}: Evaluation Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-train-final-run-train}: Training Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-warning-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-warning-color-frame, title={Package Version (Reproducibility)}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-tune-train}: Training Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-tune_lr-train}: Training Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, colback=white, titlerule=0mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, bottomtitle=1mm, arc=.35mm, left=2mm, toptitle=1mm, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, breakable]

>>>>

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-train-default}: Training Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-eval-default}: Evaluation Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-train-final-run-train}: Training Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-warning-color!10!white, colframe=quarto-callout-warning-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Package Version (Reproducibility)}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-tune-train}: Training Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-tune_lr-train}: Training Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, toprule=.15mm, breakable, bottomtitle=1mm, left=2mm, leftrule=.75mm, opacityback=0, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, arc=.35mm, opacitybacktitle=0.6, toptitle=1mm, colback=white, titlerule=0mm, rightrule=.15mm, bottomrule=.15mm]
